Geometric variational problems

### 2020-11-16 NSF2020/Description/priorsupport.tex
yny Nov15b
edited rest of proposal

\begin{wrapfigure}[9]{r}{0.56\textwidth}
\vspace{-15pt}
\definecolor{barblue}{RGB}{51,102,254}
%\renewcommand\sfdefault{phv}
%\renewcommand\mddefault{mc}
%\renewcommand\bfdefault{bc}
%\sffamily
\begin{ganttchart}[
    canvas/.append style={fill=none, draw=black!5, line width=.75pt},
        x unit =4.5mm,
        y unit chart =\baselineskip,
    hgrid style/.style={draw=black!5, line width=.75pt},
    vgrid={*1{draw=black!5, line width=.75pt}},
    title/.style={draw=none, fill=none},
    title label font=\bfseries\footnotesize, % numbers across the top
    title label node/.append style={below=3pt},
    include title in canvas=false,
    bar label font=\mdseries\footnotesize\color{black!70}, 
    % titles across the left
    %bar label node/.append style={left=2cm},
    bar/.append style={draw=none, fill=barblue},
    bar incomplete/.append style={fill=barblue},
    bar progress label font=\mdseries\footnotesize\color{black!70},
    milestone label font=\mdseries\small\color{black!70},
        milestone left shift =0.9,
        milestone right shift =0.1,
        % Don't draw group bars
        group height =0,
        group peaks height =0,
        group label font =\bfseries\small,
]{1}{12}
\gantttitle[
    title label node/.append style={below left=3pt and -6pt}
]{QUARTERS:\quad1}{1}
\gantttitlelist{2,...,12}{1} \\
%\ganttgroup{Tasks\hfill}{1}{12}\\
  \ganttbar{Specific Aim 1 (2D)}{1}{4} \\
  \ganttbar{Specific Aim 1 (3D)}{8}{12}\\
\ganttbar{Specific Aim 2}{1}{8}\\
\ganttbar{Specific Aim 3}{1}{12}\\
\ganttbar{Program management}{1}{12}
\end{ganttchart}
  \vspace{-8pt}
\caption{\footnotesize Schedule for the proposed work, measured in
  quarters from the beginning of the project.}
\label{fig:schedule}
\end{wrapfigure}
\textbf{Project management}: 
%
The success of the proposed research requires complementary expertise
and collaborative efforts in physics, applied mathematics, algorithms
and computing. Ryham has been working on mathematical modeling with a
strong analytical background. Young has been working on many areas of
computational fluid dynamics and applications to math biology for many
years. Quaife has been working on integral equation methods, fast
algorithms, and their applications to fluid dynamics for many years.
Their recent collaborative work on the HAP model in two dimensions has
provided a solid foundation on the proposed research.

@@

\textbf{Collaboration plan}: 
%
The management responsibility of this collaborative research will reside
with the lead PI (Ryham) for this endeavor. The research work is
structured to meet the tasks discussed in \S\ref{sec:proposed-work}.
%
The PIs, their postdoc and students will meet frequently on Zoom and in
person when possible. The PIs will share software packages, paper
sources, and references on a common \textsf{Git} repository. The
resulting software packages will be posted on the \textsf{Github}
software repository.

>>>>

\begin{wrapfigure}[8]{r}{0.56\textwidth}
\vspace{-19pt}
\definecolor{barblue}{RGB}{51,102,254}
%\renewcommand\sfdefault{phv}
%\renewcommand\mddefault{mc}
%\renewcommand\bfdefault{bc}
%\sffamily
\begin{ganttchart}[
    canvas/.append style={fill=none, draw=black!5, line width=.75pt},
        x unit =4.5mm,
        y unit chart =\baselineskip,
    hgrid style/.style={draw=black!5, line width=.75pt},
    vgrid={*1{draw=black!5, line width=.75pt}},
    title/.style={draw=none, fill=none},
    title label font=\bfseries\footnotesize, % numbers across the top
    title label node/.append style={below=3pt},
    include title in canvas=false,
    bar label font=\mdseries\footnotesize\color{black!70}, 
    % titles across the left
    %bar label node/.append style={left=2cm},
    bar/.append style={draw=none, fill=barblue},
    bar incomplete/.append style={fill=barblue},
    bar progress label font=\mdseries\footnotesize\color{black!70},
    milestone label font=\mdseries\small\color{black!70},
        milestone left shift =0.9,
        milestone right shift =0.1,
        % Don't draw group bars
        group height =0,
        group peaks height =0,
        group label font =\bfseries\small,
]{1}{12}
\gantttitle[
    title label node/.append style={below left=3pt and -6pt}
]{QUARTERS:\quad1}{1}
\gantttitlelist{2,...,12}{1} \\
%\ganttgroup{Tasks\hfill}{1}{12}\\
  \ganttbar{Specific Aim 1 (2D)}{1}{4} \\
  \ganttbar{Specific Aim 1 (3D)}{8}{12}\\
\ganttbar{Specific Aim 2}{1}{8}\\
\ganttbar{Specific Aim 3}{1}{12}\\
\ganttbar{Program management}{1}{12}
\end{ganttchart}
  \vspace{-10pt}
\caption{\footnotesize Schedule for the proposed work, measured in
  quarters from the beginning of the project.}
\label{fig:schedule}
\end{wrapfigure}
\textbf{Project management}: 
%
The success of the proposed research requires complementary expertise
and collaborative efforts in physics, applied mathematics, algorithms,
and computing. Ryham has been working on mathematical modeling with a
strong analytical background. Young has been working on many areas of
computational fluid dynamics and applications to math biology for many
years. Quaife has been working on integral equation methods, fast
algorithms, and their applications to fluid dynamics for many years.
Their recent collaborative work on the HAP model in two dimensions has
provided a solid foundation for the proposed research.

@@

\textbf{Collaboration plan}: 
%
The management responsibility of this collaborative research will reside
with the lead PI (Ryham) for this endeavor. The research work is
structured to meet the tasks discussed in \S\ref{sec:proposed-work}.
%
The PIs, their postdocs, and students will meet frequently on Zoom and
in person when possible. The PIs will share software packages, paper
sources, and references on a common \textsf{Git} repository. The
resulting software packages will be posted on the \textsf{Github}
software repository.
